---
title: "Querying and plotting air quality measurements"
#output: html_notebook
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Querying and plotting air quality measurements}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

## Installing package
```{r results="hide"}
if(!require(devtools)) install.packages('devtools',repos = "http://cran.us.r-project.org")
library(devtools)
url <- "https://github.com/hubert-thieriot/crea_r_package"
# devtools::install_github(url)
```
```{r results="hide"}
library(rcrea)
library(dplyr)
library(ggplot2)
library(zoo)
```

## Measurements
### Downloading measurements
Collecting measurements. By default, data is averaged by day and by city.
```{r}
meas_cities <- rcrea::measurements(city=c('Jaipur','Mumbai', 'Delhi'),
                                    average_by = 'day', # [Default: 'day'] also available NULL (raw measurements), 'hour', 'week', 'month', 'year'
                                    aggregate_at_city_level = T # [Default: TRUE] whether or not to aggregate stations data at the city level
                                    )
meas_cities
```

If you want all India data (can take a lot of time if not averaged per month or year):
```{r}
meas_india <- rcrea::measurements(country='IN', average_by = 'year')
meas_india
```

Getting data at the location level (i.e. more granular than city).
```{r}
meas_stations <- rcrea::measurements(city=c('Jaipur','Mumbai'),
                                    aggregate_at_city_level = F, # To keep it at 'location' (i.e. station) level
                                    with_metadata = T # To also collect geometry
                                    )
meas_stations
```


Let's first see how many measurements we have, and whether there are holes in time.
```{r}
rcrea::plot_measurements_count(meas_cities)
```
Black regions correspond to periods of time without any measurement in this city. Either data is not available or scraping has missed some values.


### Plotting measurements
Plotting time series of PM 2.5 per location.

Using location_id...
```{r}
rcrea::plot_measurements(meas_cities, poll=rcrea::PM25, subplot_by='city')
```
... or location name (location refers to station in OpenAQ language)
```{r}
rcrea::plot_measurements(meas_stations, subplot_by='location', color_by = 'poll')
```

Plotting city-level values per pollutant
```{r}
rcrea::plot_measurements(meas_cities, subplot_by='poll')
```
Using a 1-year rolling mean
```{r}
rcrea::plot_measurements(meas_cities, average_by='day', running_width=365, subplot_by='poll')
```

Time series of PM2.5 per location (yearly running average)
```{r}
rcrea::plot_measurements(meas_stations, poll=rcrea::PM25, running_days=365, subplot_by='location')
```

Time series of PM2.5 per city (yearly running average)
```{r}
rcrea::plot_measurements(meas_cities, poll=rcrea::PM25, running_days=365, color_by='city')
```

Monthly average
```{r}
rcrea::plot_measurements(meas_cities, poll=rcrea::PM25, average_by='month', subplot_by='city')
```

Yearly average
```{r}
rcrea::plot_measurements(meas_cities, poll=rcrea::PM25, average_by='year', subplot_by='city')
```

Evolution over years of monthly data
```{r}
rcrea::plot_measurements(meas_cities, poll=PM25, color_by='year', subplot_by='city', average_by='month')
```

Doing the same with all cities for PM10
```{r}
meas_month_all_cities <- rcrea::measurements(country='IN', average_by='month', date_from='2014-01-01', poll=PM25)
rcrea::plot_measurements(meas_month_all_cities, poll=PM25, color_by='year', subplot_by='city', average_by='month')
```
Heatmap per location with monthly data
```{r}
rcrea::plot_measurements(meas_cities, poll=PM25, subplot_by='location', type='heatmap', average_by='month')
```

Heatmap per city weekly values
```{r}
rcrea::plot_measurements(meas_cities, poll=PM25, subplot_by='city', type='heatmap', average_by='month')
```
